Molecular dynamics simulation of synchronization in driven particles

### 2020-10-14 manuscript/manuscript_ajp_2020.tex
updated script to loop f_dc by fixing sequence

\section{Molecular Dynamics Model}
\label{sec:MD}
We use a classical two-dimensional model for 
studying particle dynamics. 
Particles are confined in a two-dimensional (2D) 
simulation of area $A = L \times L$ where $L=36.5$.
An individual particle has
position $\vec{r}_i = x_i \hat{x} + y_i \hat{y}$.
We use periodic boundary conditions
such that a particle leaving the edges of the system is mapped
back to a position within the simulation 
by the rules $x_i+L=x_i$ and $y_i+L=y_i$.

@@

 We create several model light fields,
 creating a landscape of potential minima and maxima
 that modify the local force on a particle as a function of position
 $\vec{F}_{l,i} = \vec{F}_{l}(\vec{r}_i)$
 These landscape potential $V(\vec{r}) $are static,
 generating a conservative force $\vec{F}_l= -\nabla V_l(\vec{r})$
 with fixed minima and maxima
 that are periodic or quasi-periodic,
 as described in Sec.~\ref{sec:results}.
 One example of a periodic light field is
 that used in Sec.~\ref{sec:kink}
 where 
 \begin{equation}
   V_l = V_0 \cos{(N_p \pi y / L)}
 \end{equation}
 where $N_p$ are the number of troughs in the landscape,
 and $V_0$ is an adjustable parameter
 to set the depth of the troughs.

 We model particle interactions with
 the Yukawa potential $\vec{F}_{ij} = \nabla V_{ij}(r_{ij})$,
 \begin{equation}
   V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
 \end{equation}
 where $r_{ij} = |\vec{r}_i - \vec{r}_j|$.
 This is a
 screened Coulomb potential
 $E_0=2$ scales strength of repulsion
 where $E_0 = k q_1 q_2$  [CHECK scaling/units].
 $\kappa = 1/R_0$ is the screening parameter,
that screening accounts for the lengthscale at
which many particle
interactions and local environment
that reduces the interaction range of individual particles.
We fix $R_0$ to be unity in our simulation units.

Particle dynamics are
modeled with an overdamped
equation of motion
integrated with the Verlet method.
Overdamped dynamics is a common assumption in models of colloidal particles.
This is an assumption that the suspending fluid is highly viscous
and exerts a damping force on the particles equivalent
to a linear drag force.
%
The damping comes from a viscous fluid model
providing a nonconservative force,
modeled as a linear friction $F_{drag} = -\eta \vec{v}_i$
sufficient so that
the acceleration of the particle is zero.

The equation of motion we include makes both assumptions and is rearranged to reflect that. The equation of motion is not integrated for the velocity, instead it provides a direct calculation of the velocity.

A single particle has the equation of motion 
\begin{equation}
\eta \vec{v}_i = \vec{F}_{l,i} + \sum_{i \neq j}^{N} \vec{F}_{ij} + \vec{F}_{D}(t).
\end{equation}
where $\eta = 1$.
Since $\vec{a}$ is zero,
the Verlet method simplifies to 
the Euler method
$\vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t)$.

In this model the Verlet method is equivalent to the Euler method.  Euler's method is then used to calculate the position. %Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method.

@@

\subsection{Kinked system}
\label{sec:static}	% You can label sections for reference

>>>>

\section{Molecular Dynamics Model}
\label{sec:MD}
We use a classical two-dimensional model for 
studying the dynamics of $N$ interacting particles. 
Particles are confined in a two-dimensional (2D) 
simulation of area $A = L \times L$ where $L=36.5$.
An individual particle $i$ has
position $\vec{r}_i = x_i \hat{x} + y_i \hat{y}$.
We use periodic boundary conditions
such that a particle leaving the edges of the system is mapped
back to a position within the simulation 
by the rules $x_i+L=x_i$ and $y_i+L=y_i$.

@@

 We create several model light fields,
 creating a landscape of potential minima and maxima
 that modify the local force on a particle as a function of position
 $\vec{F}_{l,i} = \vec{F}_{l}(\vec{r}_i).$
 The landscape potential $V(\vec{r}) $ are static,
 generating a conservative force $\vec{F}_l= -\nabla V_l(\vec{r})$
 with fixed minima and maxima
 that are periodic or quasi-periodic,
 as described in Sec.~\ref{sec:results}.
 One example of a periodic light field is
 that used in Sec.~\ref{sec:kink}
 where 
 \begin{equation}
   V_l = V_0 \cos{(N_p \pi y / L)}
 \end{equation}
 where $N_p$ are the number of troughs in the landscape,
 and $V_0$ is an adjustable parameter
 to set the depth of the troughs.

 We model particle interactions with
 the Yukawa potential $\vec{F}_{ij} = -\nabla V_{ij}(r_{ij})$,
 \begin{equation}
   V_{ij}(r_{ij}) = \frac{E_0}{r_{ij}} e^{-\kappa r_{ij}},
 \end{equation}
 where $r_{ij} = |\vec{r}_i - \vec{r}_j|$.
 This is a
 screened Coulomb potential
 $E_0=2$ scales strength of repulsion
 where $E_0 = k q_1 q_2$  [CHECK scaling/units].
 $\kappa = 1/R_0$ is the screening parameter,
that screening accounts for the lengthscale at
which many particle
interactions and local environment
that reduces the interaction range of individual particles.
We fix $R_0$ to be unity in our simulation units.

We model the 
particle dynamics 
with an overdamped
equation of motion
integrated with the Verlet method.
Here 
the suspending fluid is highly viscous
and exerts a damping force on the particles equivalent
to a linear drag force.
%Overdamped dynamics is a common assumption in models of colloidal particles.
%This is an assumption that 
The damping comes from a viscous fluid model
providing a nonconservative force,
modeled as a linear friction $F_{drag} = -\eta \vec{v}_i$
sufficient so that
the acceleration of the particle is zero.

A single particle has the equation of motion 
\begin{equation}
\eta \vec{v}_i = \vec{F}_{l,i} + \sum_{i \neq j}^{N} \vec{F}_{ij} + \vec{F}_{D}(t).
\end{equation}
where $\eta = 1$.
The equation of motion provides a direct calculation of the velocity
of an individual particle from its location in in space.
Since $\vec{a}$ is zero,
the Verlet method simplifies to 
the Euler method,
which is used to calculate the position. %Most undergraduate students learn the Euler method in Computational Physics and Differential Equations, but don't encounter the Verlet method.
\begin{equation}
\vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t).
\end{equation}

@@

\subsection{Kinked system}
\label{sec:static}	% You can label sections for reference
We confine $N$ particles to $N-1$ troughs to create a
local high density region.
$F_{DC}/F_{AC} = 1$ [CHECK!]
